---
title: "Programming Assignment 4"
subtitle: "Project management, tidying data, HTML Presentations"
author: "Dine Mamadou"
date: "2018/3/6"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: TRUE
---
(1-4).Data overview


```{r load_library, message=FALSE, warning=FALSE, include=TRUE}
library(tidyverse)
library(xaringan)
library(plot3D)
library(ggfortify)


fricatives <- read.csv("fricatives.csv")



str(fricatives)

```
---
5.Tidy data sample
  
```{r}
my_data1 <- fricatives %>%
  select(., alveolar = s_cog, postAlveolar = sh_cog) %>%
  gather(., key = phoneme, value = centerOfGravity) 

my_data2 <- fricatives %>%
  select(., alveolar = s_skewness, postAlveolar = sh_skewness) %>%
  gather(., key = phoneme, value = skewness)

```

---
6.Descriptive Stats

```{r, fig.width = 10, fig.retina = 2}
fricatives %>%
  select(., -obs) %>%
  summary() %>%
  knitr::kable(., digits = 2)


```


---
7.COG as a function of phoneme (Boxplot)

```{r, fig.width = 10, fig.retina = 2}
my_data1 %>%
  ggplot(., aes(x = phoneme, y = centerOfGravity)) +
    geom_boxplot()
```

---
7.1 Skewness as a function of phoneme (Jitter)

```{r, fig.width = 10, fig.retina = 2}
my_data2 %>%
  ggplot(., aes(x = phoneme, y = skewness)) +
  geom_jitter() 
```
---
8.COG as a function of Skewness for [s] and scatter plot

8.1 The data
```{r}
phonemeS <- fricatives %>%
  select(., cog = s_cog, skewness = s_skewness) 

head(phonemeS)

```
---
8.2 The model 

```{r, fig.width = 10, fig.retina = 2}
lm(cog ~ skewness, data = phonemeS)
mod <- lm(cog ~ skewness, data = phonemeS)


```
---
8.3 Model summary
```{r}
summary(mod)
mean(mod$residuals)


```
---
9 Scatterplot
```{r}

mod %>%
  ggplot(., aes(x = cog, y = skewness)) +
  geom_point() +
  geom_smooth()
  

```
---

10.Model diagnistics

10.1 Autoskedasticity
```{r, fig.width = 10, fig.retina = 2}

lmtest::dwtest(mod)

```
---
10.2 Normality
```{r}
autoplot(mod)

```
---
10.3 Autocorrelation of residuals
```{r, fig.width = 10, fig.retina = 2}

acf(mod$res)
```
---
11.Interpretation of the results

The mean of the fitted model is 1.13 to the -10th power. The plot of the skewness as a function of the phoneme shows on one hand that the anteriority of the phoneme determines the direction of its skewness; that is, alveolars /s/ are negatively skewed while post-alveolars /sh/ are positively skewed. On the other hand, the center of gravity is higher for alveolars than it is for post-alveolars.

The scatterplot shows a positive correlation between skewness and center of gravity (cog) for the phoneme /s/. Skewness is shown to be a good predictors of cog as it significantly affect the model at p < 0.001. 
